Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-10 acknowledgments.tex
updated nathan's initials

This work has been supported by the National Science Foundation by
grants
AAG-0808184 (DRR),
AAG-1109008 (DRR),
ACI-9619019 (MLN),
ASC-9313135 (MLN),
AST-9803137 (MLN), 
AST-0307690 (MLN), 
AST-0407176 (RC),
AST-0407368 (SS, EJH),
AST-0507521 (RC) 
AST-0507717 (MLN), 
AST-0507768 (AK),
AST-0607675 (AK)
AST-0702923 (EJH),
AST-0707474 (BDS), 
AST-0708960 (MLN), 
AST-0807215 (JB),
AST-0808184 (MLN, AK),
AST-0908819 (BWO) 
AST-0955300 (NG),
AST-1008134 (GB) 
AST-1009802 (JSO), 
AST-1102943 (MLN)
AST-1106437 (JB),
AST-1210890 (GB),
AST-1211626 (JW),
OCI-0832662 (BWO, MLN),
OCI-0941373 (BWO),
PHY-1104819 (MLN, JB),
the CI TraCS fellowship (OCI-1048505; MJT),
and the Graduate Research Fellowship program (NG; SJS).

>>>>

This work has been supported by the National Science Foundation by
grants
AAG-0808184 (DRR),
AAG-1109008 (DRR),
ACI-9619019 (MLN),
ASC-9313135 (MLN),
AST-9803137 (MLN), 
AST-0307690 (MLN), 
AST-0407176 (RC),
AST-0407368 (SS, EJH),
AST-0507521 (RC) 
AST-0507717 (MLN), 
AST-0507768 (AK),
AST-0607675 (AK)
AST-0702923 (EJH),
AST-0707474 (BDS), 
AST-0708960 (MLN), 
AST-0807215 (JB),
AST-0808184 (MLN, AK),
AST-0908819 (BWO) 
AST-0955300 (NJG),
AST-1008134 (GB) 
AST-1009802 (JSO), 
AST-1102943 (MLN)
AST-1106437 (JB),
AST-1210890 (GB),
AST-1211626 (JW),
OCI-0832662 (BWO, MLN),
OCI-0941373 (BWO),
PHY-1104819 (MLN, JB),
the CI TraCS fellowship (OCI-1048505; MJT),
and the Graduate Research Fellowship program (NJG; SJS).
